Analysis plan

### 2023-09-27 04. Analysis/scripts/04-02-abstract.Rmd
Update 04-02-abstract.Rmd

prep_d_05 %>% view()
```

@@

>>>>

prep_d_05
```

@@

## small

```{r}
p_3 <- 
  prep_d_06 %>% 
  ggplot(aes(x = .cluster_5, y = value, fill = name)) +
  geom_bar(stat = "identity") +
  labs(title = "Work and leave per pay period") +
  ylab("Days per pay period") +
  scale_y_continuous(labels = scales::comma) +
  oescolorrrs::scale_fill_oes() +
  oescolorrrs::scale_color_oes() +
  theme_light() +
  theme(
    legend.position = "bottom",
    legend.title = element_blank(),
    plot.title = element_text(hjust = 0.5,
                              size = 10),
    axis.title.y = element_text(size = 8, vjust = -2),
    axis.title.x = element_blank(),
    axis.text = element_text(size = 7),
    legend.text = element_text(size = 7)
    )

```{r}
ggsave(filename = fp, plot = p_3, width = 3, height = 3, units = "in")
```
